Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest

### 2024-10-20 paper/paper.qmd
committing text changes to paper.qmd

# Results {#sec-results}
## Predicted Election Winner By State
@fig-statemap shows the predicted winner of the 2024 US Presidential Election by state on a map [@usmap], based on a logistic regression model using aggregated polling data for Donald Trump and Kamala Harris. States where Trump is predicted to win are shown in red, while states where Harris is predicted to win are displayed in blue. States in gray represent missing or incomplete polling data, where predictions were not possible. According to the model, Trump is expected to win key states, including Florida, Missouri, and Montana, while Harris is forecasted to lead in Michigan, Virginia, and Pennsylvania.
```{r}
#| label: fig-statemap
#| fig-cap: Predicted Winner of 2024 US Presidential Election by State
#| echo: false
#| warning: false
#| message: false
#| cache: false

@@

# Map visualization showing predicted winner by state
plot_usmap(data = state_average, values = "predicted_winner", regions = "states") +
  scale_fill_manual(values = c("Trump" = "red", "Harris" = "blue"), name = "Predicted Winner") +
  theme(legend.position = "right")
```
The results highlight the geographic divide between the two candidates. Trump is predicted to perform well in southern and midwestern states, where his polling averages are significantly higher. Harris, on the other hand, is projected to win in the Midwest and along the East Coast, with stronger polling percentages in traditionally Democratic-leaning regions.

>>>>

# Results {#sec-results}
## Predicted Election Winner By State
@fig-statemap shows the predicted winner of the 2024 US Presidential Election by state on a map [@usmap], based on a logistic regression model using aggregated polling data for Donald Trump and Kamala Harris. States where Trump is predicted to win are shown in red, while states where Harris is predicted to win are displayed in blue. States in gray represent missing or incomplete polling data, where predictions were not possible. 
```{r}
#| label: fig-statemap
#| fig-cap: Predicted Winner of 2024 US Presidential Election by State
#| echo: false
#| warning: false
#| message: false
#| cache: false

@@

# Map visualization showing predicted winner by state
plot_usmap(data = state_average, values = "predicted_winner", regions = "states") +
  scale_fill_manual(values = c("Trump" = "red", "Harris" = "blue"), name = "Predicted Winner") +
  theme(legend.position = "right")
```

According to the model, Trump is expected to win key states, including Florida, Missouri, and Montana, while Harris is forecasted to lead in Michigan, Virginia, and Pennsylvania.The results highlight the geographic divide between the two candidates. Trump is predicted to perform well in southern and midwestern states, where his polling averages are significantly higher. Harris, on the other hand, is projected to win in the Midwest and along the East Coast, with stronger polling percentages in traditionally Democratic-leaning regions.
